Pulsar Acceleration Shifts from nearby Supernova Explosion

### 2016-04-29 draft3_1C.tex

Here $w_0 = w_e(0)$ is the frequency observed on earth at the moment when we see the SN explosion. 
In the second line, the final term is what is calculated\footnote{See Eq (23) in \cite{OluPie13}. We have replaced $b$ in that equation with $r_p \sin \theta$ to be consistent with notation used in this paper.} in \cite{OluPie13} and this incorporates the effect of the pulses crossing the neutrino shell. In going to the final line we have simply set $t = r_p (1 - \cos \theta)$ as the effects in the second line will build up to that time and then will remain constant. The final term in the third line is just the acceleration of the pulsar in the new metric after shell crossing.

>>>>

Here $w_0 = w_e(0)$ is the frequency observed on earth at the moment when we see the SN explosion. The first line is before we observe the SN explosion, so the only contribution to the change in the observed frequency comes from the gravitational pull to the SN, which is a term linear in $t$. The same gravitational pull is still present in the second line, but we need to include the effect from photons crossing the neutrino shell derived in \cite{OluPie13}\footnote{See Eq (23) in \cite{OluPie13}. We have replaced $b$ in that equation with $r_p \sin \theta$ to be consistent with notation used in this paper.}, which is the last term. Finally in the last line, the pulsar also enters the geometry inside the neutrino shell, thus no more time-dependent effect from shell-crossing. The accumulated effect remains which is expressed as the two time-independent terms. The last term is still the gravitational pull, but with a slightly smaller mass $M_f$ and with $t$ set to $(t-r_p(1-\cos\theta))$.
